---
title: "Introduction to czplots"
author: "Chenhao Zhou"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    css: custom.css
vignette: >
  %\VignetteIndexEntry{Introduction to czplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Welcome to `czplots`! This R package provides functions for fast and intuitive analysis of scRNA-seq data. Here, we will go through a quick tutorial on how to use these functions.

To get started, this package incudes a trimmed test dataset of 2,000 mouse skin T cells derived from [Zhou et al 2021](https://academic.oup.com/immunohorizons/article/5/2/102/7820221?login=true). we will use this test dataset to demonstate key functions within this package.

``` r
library(czplots)

#load test dataset
data(skin_tcell)

skin_tcell@meta.data
```



## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
