---
title: "Introduction to czplots"
author: "Chenhao Zhou"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    css: custom.css
vignette: >
  %\VignetteIndexEntry{Introduction to czplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# Load required packages
library(czplots)
library(Seurat)
# Load the dataset once
data(skin_tcell)
```
Welcome to `czplots`! This R package provides functions for fast and intuitive analysis of scRNA-seq data. Here, we will go through a quick tutorial on how to use these functions.

To get started, this package incudes a trimmed test dataset of 2,000 mouse skin T cells downloaded from [Zhou et al 2021](https://academic.oup.com/immunohorizons/article/5/2/102/7820221?login=true). we will use this test dataset to demonstate key functions within this package.

``` {r, echo=TRUE, warning=FALSE,}
library(czplots)
library(Seurat)

#load test dataset
data(skin_tcell)

```

First, let’s take a look at the dataset. It includes 9 skin T cell clusters (C0–C8) derived from two mouse groups: K14E7 transgenic mice and wildtype C57BL/6 mice.

``` {r, echo=TRUE,warning=FALSE,}
skin_tcell@meta.data[1:2,]

unique(skin_tcell@meta.data$tissue)

unique(skin_tcell@meta.data$seurat_clusters)

```

## Cell type composition analysis 

A common starting point in most analyses is identifying which cell types are enriched in each group, condition, or disease. This package provides a fast and convenient way to calculate the proportion of each cluster within each group and visualize the differences using a bar chart. To use this function, the user must specify two arguments: (1) group and (2) level. Examples are provided below."

```{r, fig.show='asis'}
countpercluster(skin_tcell,group="tissue",level<-c("skin_E7g","skin_C57g"))

```

## Annotation

This function allows users to quickly generate the heatmap plots summarising expression pattern of selected gene markers.
Plot 1 shows mean expression of each marker. Plot 2 shows percentage of cells that have non-zero expression of each marker. 

```{r, fig.show='asis',message = FALSE, warning=FALSE}
annotation_heatmap(skin_tcell,gene=c("Cd44","Cd69","Itgae","Ccr7","Il7r","Tbx21","Ifng","Il2","Gata3","Il4","Il5","Foxp3","Ctla4","Pdcd1","Tigit","Il2ra","Gzmb","Il10","Il17a","Cxcr5","Bcl6","Cd8a","Cd4"),group="seurat_clusters")

```




